%-------------------------
% Resume in Latex
% Author : Harshit Agarwal
% Based on: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article} % 10pt for better fit

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins - optimized for 1 page
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure machine readable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, nosep]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

% -------------------- HEADING --------------------
\begin{center}
    \textbf{\Huge \scshape Harshit Agarwal} \\ \vspace{4pt}
    \small
    \faEnvelope \hspace{1pt} \href{mailto:aharshit123456@gmail.com}{aharshit123456@gmail.com} $|$ 
    \faPhone \hspace{1pt} +91-9776076583 $|$ 
    \faLinkedin \hspace{1pt} \href{https://www.linkedin.com/in/aharshit123456/}{in/aharshit123456} $|$
    \faGithub \hspace{1pt} \href{https://github.com/aharshit123456}{github/aharshit123456} $|$
    \faGlobe \hspace{1pt} \href{https://aharshit123456.github.io}{aharshit123456.dev}
\end{center}

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, JavaScript/TypeScript, Java, Go, Kotlin, C\#, SQL} \\
     \textbf{Frameworks \& Libraries}{: FastAPI, Flutter, React, Next.js, PyTorch, TensorFlow, ROS2, ComfyUI} \\
     \textbf{Cloud \& DevOps}{: AWS (EKS, SageMaker), Docker, Kubernetes, Terraform, GitOps, CI/CD (Fastlane/Actions)} \\
     \textbf{Databases \& Systems}{: PostgreSQL, Redis, Supabase, Low-Latency Systems, Distributed Architecture}
    }}
 \end{itemize}
 \vspace{-12pt}

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FamCARE}{Apr 2025 -- Present}
      {Lead Full-Stack Architect \& Systems Lead}{HSR Layout, Bangalore}
      \resumeItemListStart
        \resumeItem{Architected and delivered the complete full-stack ecosystem, scaling a modular \textbf{FastAPI backend} and \textbf{3 cross-platform Flutter apps} from zero to production with \textbf{500+ commits} across 4 repositories.}
        \resumeItem{Engineered a high-throughput API architecture verified via stress testing to handle \textbf{2,000+ requests/minute} and \textbf{100 concurrent users} with a \textbf{100\% success rate} for core operational flows.}
        \resumeItem{Engineered a modular monolith architecture with \textbf{15+ decoupled services} (modules) designed for the \textbf{Strangler Pattern}, managing complex \textbf{Order/Booking} flows, \textbf{Razorpay} payments, and a multi-channel notification engine (\textbf{FCM}, \textbf{Fast2SMS}, \textbf{MSG91}).}
        \resumeItem{Optimized operational velocity by \textbf{70\%} using \textbf{Fastlane CI/CD} and automated caregiver background verification via \textbf{SpringVerify API}, reducing turnaround time from days to minutes.}
      \resumeItemListEnd

    \resumeSubheading
      {Endorphind}{Jan 2026 -- Present}
      {Founding SDE (AI \& Systems)}{Indiranagar, Bangalore}
      \resumeItemListStart
        \resumeItem{Engineered SOTA generative video pipelines using Wan 2.2/2.6 and LatentSync; integrated ElevenLabs and F5 for high-fidelity voice cloning, and developed custom ComfyUI nodes for automated media production.}
        \resumeItem{Architected "LangLearn," an LLM-driven educational platform; led technical roadmap and project scoping.}
        \resumeItem{Leading a team of 3 SDEs via Agile/Scrum; overseeing client architectures for Video Diffusion and AI chatbots.}
      \resumeItemListEnd
      
    \resumeSubheading
      {shoppin' — USAR Commerce Technologies}{Dec 2024 -- Nov 2025}
      {Founding ML Engineer (AI/Infra)}{Gurgaon, HR}
      \resumeItemListStart
        \resumeItem{Productionized AI systems for fashion search (3-4 crore items) using CLIP/VLLM embeddings and Diffusion VTON.}
        \resumeItem{Engineered distributed media pipelines on AWS SageMaker; automated scraping for 200+ partner stores.}
        \resumeItem{Architected AWS EKS infrastructure with Terraform and GitOps, ensuring disaster recovery and high availability.}
      \resumeItemListEnd

    \resumeSubheading
      {SMLab, NISER}{May 2024 -- Nov 2024}
      {Research Intern (Robotics \& Sensors)}{Jatni, OD}
      \resumeItemListStart
        \resumeItem{Crafted iPhone-Drone Sensor Calibration system with \textbf{180Hz} data transmission; built Web Console for self-driving motorcycle (ROS2) handling 25+ sensors with \textbf{0.2ms} latency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% -------------------- EDUCATION --------------------
\vspace{-8pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kalinga Institute of Industrial Technology (KIIT)}{May 2027}
      {B.Tech in Computer Science and Engineering}{CGPA: 9.30/10.0}
  \resumeSubHeadingListEnd

% -------------------- PROJECTS \& PUBLICATIONS --------------------
\vspace{-8pt}
\section{Projects \& Publications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{A Hybrid Transformer-LSTM Framework for Physiotherapy Recognition}}{FACEIT 2026}
    \resumeProjectHeading
      {\textbf{Open-source Python Library for Human Gait Analysis (gaitSetPy)}}{FICTA 2026}
    \resumeProjectHeading
      {\textbf{Deep Neural Frameworks for Fall Risk Assessment}}{Elsevier - AI in Medicine}
    \resumeProjectHeading
      {\textbf{NVD Exploitability Toolkit} $|$ \emph{Hugging Face, PyTorch}}{ICANTCI 2025}
      \resumeItemListStart
        \resumeItem{Fine-tuned DistilBERT/GPT2 on 56k+ vulnerabilities; achieved \textbf{85.6\% accuracy} in exploitability prediction.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% -------------------- LEADERSHIP \& AWARDS --------------------
\vspace{-8pt}
\section{Leadership \& Awards}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{KIIT E-Cell} $|$ RnD Intern: Organized hackathons (\$150K prize pool) and managed 120+ teams.}{2024}
    \resumeProjectHeading
      {\textbf{Microsoft Learn Student Ambassador} $|$ AI-ML Volunteer: Led ForgeTube AI video gen system.}{2025}
    \resumeProjectHeading
      {\textbf{Awards}: KIIT Merit Scholarship (Top 1000 Rank), Oxford-Cambridge Research Scholarship.}{}
  \resumeSubHeadingListEnd

\end{document}
